Natural selection in the Health and Retirement Study

### 2023-11-29 hrs-selection.qmd

rand <- rand |> 
  select(ethnicity, all_of(pgs), all_of(old_pgs), 
         all_of(pcs), weight, raevbrn, rlrs,
         raedyrs, r10sibs, edu, income_med, married, agefb, agefbn,
         rabyear, born, raehsamp, raestrat, parent_weight, ragender,
         adhd_score, neurot, r10diabe, r10hearte, r10cesd, age_smoked,
         anxiety, r10cogtot, rlrs_div_h10gkid, child_weight)
# added my grandkid rlrs

>>>>

rand <- rand |> 
  select(ethnicity, all_of(pgs), all_of(old_pgs), 
         all_of(pcs), weight, raevbrn, rlrs,
         raedyrs, r10sibs, edu, income_resid, income_med, married, 
         agefb, agefbn,
         rabyear, born, raehsamp, raestrat, parent_weight, ragender,
         adhd_score, neurot, r10diabe, r10hearte, r10cesd, age_smoked,
         anxiety, r10cogtot, rlrs_div_h10gkid, child_weight)
# added my grandkid rlrs
